---
title: "PIE-3P analyses"
author: "Amanda Mae Woodward"
date: "2/26/2020"
output: html_document
---
```{r}
library(lmerTest)
library(expss)
library(Rmisc)
library(plyr)
library(dplyr)
library(car)
library(doBy)
library(tidyverse)
library(ggplot2)
library(lme4)
library(RColorBrewer)

```

```{r}
dat<- read.csv("~/Desktop/PIE-3P Analyses/PIE3P-dataclean.csv")
```

#Overall Analysis
##Question: Do children detect social exclusion more after the exclusion game than the inclusion game? 
Note: I used the **first** detection for this analysis because it was the one not influenced by the experimenter's feedback. 

```{r}
summary(dat$Exclusion_D1[dat$Inclusion_D1=="play"]) #This summary gives us the children who answered the inclusion question correctly and the exclusion question incorrectly and correctly
summary(dat$Exclusion_D1[dat$Inclusion_D1=="watch"])# This summary gives us the children who answered the inclusion questionin correctly and the exclusion question incorrectly and correctly 

ExclusionTotal<- c(4,61)
InclusionTotal<- c(0,4)
detectMatrix<-as.matrix(rbind(ExclusionTotal,InclusionTotal))
detectMatrix
mcnemar.test(detectMatrix)
```
**Interpretation:** Overall, children detect social exclusion when it is present, more often than when it is not 

###By Age Group (pre-registration)
```{r, include=FALSE}
Younger<-subset(dat, dat$ageGroup==3 |dat$ageGroup==4)
Older<-subset(dat, dat$ageGroup==5 | dat$ageGroup==6)
```
####Younger
```{r}
summary(Younger$Exclusion_D1[Younger$Inclusion_D1=="play"])
summary(Younger$Exclusion_D1[Younger$Inclusion_D1=="watch"])
youngerInclusion<-c(3,29)
youngerExclusion<-c(0,3)
youngerMatrix<- as.matrix(rbind(youngerInclusion,youngerExclusion))
mcnemar.test(youngerMatrix)
```
**Interpretation:** Younger children detect exclusion when it is present more than when it is not present
####Older
```{r}
summary(Older$Exclusion_D1[Older$Inclusion_D1=="play"])
summary(Older$Exclusion_D1[Older$Inclusion_D1=="watch"])
olderExclusion<- c(1,32)
olderInclusion<- c(0,1)
olderMatrix<-as.matrix(rbind(olderExclusion, olderInclusion))
mcnemar.test(olderMatrix)
```
**Interpretation:** Older children detect exclusion when it is present more than when it is not present

##Overall, do Children evaluate includers as nicer than excluders? 
```{r}
wilcox.test(dat$ExclusionNiceScale,dat$InclusionNiceScale, paired=TRUE)
meanStd<- function(col){
  print(c(mean(col), sd(col)))
}
meanStd(dat$ExclusionNiceScale)
meanStd(dat$InclusionNiceScale)
```
**Interpretation:** Children rate includers as nicer than excluders

###By Age Group

####Younger
```{r}
wilcox.test(Younger$ExclusionNiceScale, Younger$InclusionNiceScale, paired = TRUE, alternative = "less")
meanStd(Younger$ExclusionNiceScale)
meanStd(Younger$InclusionNiceScale)
```
**Interpretation:** Overall, younger children indicate that includers are nicer than excluders 

####Older Age Group
```{r}
wilcox.test(Older$ExclusionNiceScale, Older$InclusionNiceScale, paired=TRUE)
meanStd(Older$ExclusionNiceScale)
meanStd(Older$InclusionNiceScale)
```
**Interpretation:** Older children rated the includer as nicer than the excluder

##Overall, do children prefer to play with the inclusive puppet over the exclusive puppet?
```{r}
cro(dat$playQ)
binom.test(49,69)
```
**Interpretation:** Overall, children prefer to play with the includer over the excluder

###By age group

####Younger
```{r}
cro(Younger$playQ)
binom.test(19,35, alternative="greater")
```
**Interpretation:** Younger children do not have a preference for the includer over the excluder

####Older
```{r}
cro(Older$playQ)
binom.test(30,34)
```
**Interpretation:** Children preferred to play with the including puppet over the excluding puppet 

##Overall, do children answer the memory check question correctly?
```{r}
cro(dat$memCheck)
binom.test(67,69)
```
**Interpretation:** Children identified the inclusive puppet more often than chance

###By age group
####Younger
```{r}
cro(Younger$memCheck)
binom.test(33,35)
```
**Interpretation:** Younger children identified the inclusive puppet more than chance. 

####Older
```{r}
cro(Older$memCheck)
binom.test(34,34)
```
**Interpretation:** older children identified the inclusive puppet more than chance

##Does age predict whether children will detect social exclusion across game types?

```{r}
datSub<-cbind.data.frame(dat[,2:5],dat[,9:11], dat[,14],dat[,18])
colnames(datSub)[8:9]<-c("Exclusion_D1","Inclusion_D1")
detectLong<-pivot_longer(datSub,col= c("Exclusion_D1", "Inclusion_D1"), names_to = "Game", values_to= "Response") 
detectLong$Response<- as.factor(detectLong$Response)
levels(detectLong$Response)<- c(0, 1)
detectLong$Response<- as.numeric(levels(detectLong$Response))[detectLong$Response]
detectLong$Game<-as.factor(detectLong$Game)
detectLong$subj<-as.factor(detectLong$subj)
detectLong$order<-as.factor(detectLong$order)
detectLong$ecolor<- as.factor(detectLong$ecolor)
detectLong$eside<-as.factor(detectLong$eside)
detectLong$sex<-as.factor(detectLong$sex) 
detectLong$ageGroup<-as.factor(detectLong$ageGroup)
```
###Preliminary Model(s)
```{r}
detectLong$ageScale<-scale(detectLong$ageMonths)

glm1<- glmer(Response~ Game+ageScale+sex+ecolor+eside+order+(1|subj), data=detectLong, family=binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glm1)
```
**Interpretation:** Model failed to converge. No counterbalancing factors significantly predicted children's choices. 

###Main Model
```{r}
glm2<- glmer(Response~ ageScale*Game+(1|subj), data=detectLong, family=binomial(link = "logit"),control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glm2)

```
**Interpretation:** Age did not significantly predict whether children detected social exclusion. Game was the only significant predictor. 

#####Notes on this section:
```{r}
ageDect<-summarySEwithin(data=detectLong, measurevar= "Response", betweenvars="ageGroup", withinvars="Game", idvar="subj", conf.interval=0.95)
levels(ageDect$Game)<- c("Exclusion", "Inclusion")
"note: not using this version b/c can't place space the way i want to"
levels(ageDect$ageGroup)<-c(" 3 \nyears", " 4 \nyears"," 5 \nyears", " 6 \nyears")

ggsave("PIE3P-ExclusionDetection2.tiff", units="in", width=10, height=8, dpi=300)
ggplot(detectLong, aes(ageMonths,Response,group=Game) )+geom_point(aes(fill=Game),size=4,pch=21,color="black") +theme_classic()+geom_smooth(method="lm",aes(color=Game), size=1.5)+scale_fill_manual(values=c("#045a8d", "#74a9cf"))+scale_color_manual(values=c("#045a8d", "#74a9cf")) +theme(legend.title=element_blank()) + xlab("Age (in months)")+ ylab("Children's Detection of Social Exclusion") + theme(plot.title=element_text(family="Times New Roman", face="bold", size=20))+ theme(text = element_text(size=20, family ="Times New Roman", face="bold"))
dev.off()
```

##Does age predict children's niceness ratings? 
```{r }
datSub<-cbind.data.frame(dat[,2:5],dat[,9:11], dat[,21],dat[,25])
colnames(datSub)[8:9]<-c("ExclusionNice","InclusionNice")
niceLong<-pivot_longer(datSub,col= c("ExclusionNice", "InclusionNice"), names_to = "Game", values_to = "Nice") 

```
###Preliminary Model(s)
```{r}
glm1N<- lmerTest::lmer(Nice~ Game+ageMonths+sex+ecolor+eside+order+(1|subj), data=niceLong)
summary(glm1N)
```
**Interpretation:**  No counterbalancing factors significantly predicted children's choices.Character evaluated significantly predicted children's niceness ratings.

###Main Model
```{r}
glm2N<- lmerTest::lmer(Nice~ Game*ageMonths+(1|subj), data=niceLong)
summary(glm2N)
```
**Interpretation:** Game significantly predicted children's niceness ratings. Game and age interacted to predict children's niceness ratings. Older children rated includers as nicer. 

#simple slope on Nice
```{r}
E<-subset(niceLong, niceLong$Game=="ExclusionNice")
I<- subset(niceLong, niceLong$Game=="InclusionNice")

glm2NE<- lm(Nice~ ageMonths, data=E)
summary(glm2NE)
glm2NI<- lm(Nice~ ageMonths, data=I)
summary(glm2NI)
```

```{r}
levels(niceLong$Game)<- c("Excluding Character", "Including Character")
ggsave("PIE3P-Nicenessratings2020-11-02.tiff", units="in", width=10, height=8, dpi=300)
ggplot(niceLong, aes(ageMonths,Nice,group=Game))+geom_point(aes(fill=Game),size=4,pch=21,color="black") +theme_classic()+geom_smooth(method="lm",aes(color=Game), size=1.5, alpha=.45)+scale_fill_manual(values=c("#000000","#FFFFFF"))+scale_color_manual(values=c("#000000","#FFFFFF")) +theme(legend.title=element_blank(),axis.ticks = element_line(colour = "black", size = 1)) + xlab(" ")+ ylab(" ")+theme(legend.position= "none",plot.title=element_text(family="Arial", face="bold", size=20))+ theme(text = element_text(size=20, family ="Arial", face="bold"))+scale_y_continuous(breaks=seq(1,6,1))
dev.off()

ggsave("PIE3P-Nicenessratings2021-02-09b.tiff", units="in", width=10, height=8, dpi=300)
ggplot(niceLong, aes(ageMonths,Nice,group=Game))+geom_point(aes(fill=Game),size=4,pch=21,color="black", position=position_jitter(width=.1, height=.1)) +theme_classic()+geom_smooth(method="lm",aes(color=Game), size=1.5, alpha=.45)+scale_fill_manual(values=c("#000000","#FFFFFF"))+scale_color_manual(values=c("#000000","#FFFFFF")) +theme(legend.title=element_blank(),axis.ticks = element_line(colour = "black", size = 1)) + xlab(" ")+ ylab(" ")+theme(legend.position= "none",plot.title=element_text(family="Arial", face="bold", size=20))+ theme(text = element_text(size=20, family ="Arial", face="bold"))+scale_y_continuous(breaks=seq(1,6,1)) 
dev.off()
```
**Interpretation of interaction:** Children's' niceness ratings of inclusive players stays relatively stable across age, but children rate the exclusive puppet more negatively across age. 

####Follow up analyses
```{r}
wilcox.test(dat$ExclusionNiceScale[dat$ageGroup==3], dat$InclusionNiceScale[dat$ageGroup==3], paired=TRUE)
```
```{r}
wilcox.test(dat$ExclusionNiceScale[dat$ageGroup==4], dat$InclusionNiceScale[dat$ageGroup==4], paired=TRUE)
```
```{r}
wilcox.test(dat$ExclusionNiceScale[dat$ageGroup==5], dat$InclusionNiceScale[dat$ageGroup==5], paired=TRUE)
```
```{r}
wilcox.test(dat$ExclusionNiceScale[dat$ageGroup==6], dat$InclusionNiceScale[dat$ageGroup==6], paired=TRUE)
```

##Does age predict children's play choices? 
###Preliminary Model(s)
```{r}
dat$playQ<- as.factor(dat$playQ)
levels(dat$playQ)<-c(0,1)
dat$playQ2<- as.numeric(levels(dat$playQ))[dat$playQ]

glm1P<- glm(playQ~ ageMonths+sex+ecolor+eside+order, data=dat, family=binomial)
summary(glm1P)

lm1P<- glm(playQ~ ageMonths*ecolor, data=dat, family=binomial)
summary(glm1P)
```
**Interpretation:** Age in months and color of the excluder predicted children's play choices

```{r}
cro(dat$playQ,dat$ecolor)
binom.test(14,20,alternative="greater")
```
Note: children were more likely to play with the excluder when they wore a blue shirt. 

###Main Model
```{r}
glm2P<- glm(playQ~ ageMonths, data=dat, family=binomial)
summary(glm2P)
```
**Interpretation:** Age predicted children's play choices. Older children were more likely to play with the includer than the excluder
```{r}
agePlay<-summarySE(data=dat, measurevar= "playQ2", groupvars="ageGroup",  conf.interval=0.95)
agePlay$ageGroup<-as.factor(agePlay$ageGroup)
levels(agePlay$ageGroup)<-c(" 3 \nyears", " 4 \nyears", " 5 \nyears", " 6 \nyears")

ggsave("PIE3P-PlayChoice2021-02-09.tiff", units="in", width=10, height=8, dpi=300)
ggplot(dat, aes(x=ageMonths, y=playQ2))+geom_point(size=4,aes(fill=playQ),pch=21,color="black", position=position_jitter(width=.02, height=.02))+stat_smooth(method="glm", method.args=list(family="binomial"), color="black", alpha=.45)+theme_classic()+scale_fill_manual(values=c("#000000","#FFFFFF"))+theme(legend.title=element_blank()) + xlab("")+  ylab("")+theme(legend.position="none",plot.title=element_text(family="Arial", face="bold", size=20))+ theme(text = element_text(size=20, family ="Arial", face="bold"),axis.ticks = element_line(colour = "black", size = 1))+theme(legend.position = "none")+scale_y_continuous(breaks=seq(0,1,1))
dev.off()
```

####follow up analyses
```{r}
cro(dat$playQ, dat$ageGroup)
binom.test(7,16)
binom.test(12,19)
binom.test(15,17)
binom.test(15,17)
```

##Does age predict children's memory check responses? 
###Preliminary Model(s)
```{r}
dat$memCheck<-as.factor(dat$memCheck)
levels(dat$memCheck)<-c(0,1)
dat$memCheck<-as.numeric(levels(dat$memCheck))[dat$memCheck]
dat$order<-as.factor(dat$order)
dat$eside<-as.factor(dat$eside)
dat$ecolor<- as.factor(dat$ecolor)
dat$sex<- as.factor(dat$sex)
glm1M<- glm(memCheck~ ageMonths+sex+ecolor+eside+order, data=dat, family=binomial)
summary(glm1M)
```
**Interpretation:** model did not converge (so few children answered the memory check incorrectly that can't really anyalyze)

###Main Model
```{r}
glm2P<- glm(memCheck~ ageMonths, data=dat, family=binomial)
summary(glm2P)
```
**Interpretation:** Age did not predict children's memory check responses
```{r}
ageMem<-summarySE(data=dat, measurevar= "memCheck", groupvars="ageGroup",  conf.interval=0.95)
ageMem$ageGroup<-as.factor(ageMem$ageGroup)
levels(ageMem$ageGroup)<-c(" 3 \nyears", " 4 \nyears", " 5 \nyears", " 6 \nyears")
ggsave("PIE3P-MemCheck.tiff", units="in", width=10, height=8, dpi=300)
ageMem$ageGroup2<- as.character(ageMem$ageGroup)
ggplot(ageMem,aes(ageGroup2,memCheck))+geom_bar(stat="identity",position=position_dodge2(width= 1, preserve=c( "single"),padding = 2), color="black", fill="#D6D6D6")+scale_y_continuous(breaks=seq(0,1,.25))+ theme_classic()+geom_errorbar(size=1, width=.1,position=position_dodge(1), aes(ymin=memCheck-ci, ymax=memCheck+ci))+ geom_hline(yintercept=.5,color="red",linetype="dashed",size=1.5)+xlab("")+ ylab("Proportion Answering Accurately")+theme(plot.title=element_text(family="Arial", face="bold", size=20))+ theme(text = element_text(size=20, family ="Arial", face="bold"),axis.ticks = element_line(colour = "black", size = 1))+theme(legend.position = "none")
dev.off()
```

##Exploratory Analyses
What reason do children give for their play choice? 
```{r}
cro(dat$playAvoid)
binom.test(56,69)
```
**Interpretation:** children overwhelmingly choose a play mate because they think they will play with them (e.g. play not avoid)

By age
###younger
```{r}
cro(Younger$playAvoid)
binom.test(28,35)
```

###older
```{r}
cro(Older$playAvoid)
binom.test(28,34)
```
```{r}
cro(dat$playAvoid)
d1<- subset(dat, dat$playAvoid!="both")
glm2Pp<- glm(playAvoid~ageMonths+sex+ecolor+eside+order, data=d1, family=binomial)
summary(glm2Pp)
glm2Pp<- glm(playAvoid~ageMonths, data=d1, family=binomial)

```
**Interpretation:** both older and younger children are choosing to play with the person because they think they are more likely to play with them

is there a difference between play choice and reasoning? 
```{r}
summary(dat$playAvoid[dat$playQ==1])
summary(dat$playAvoid[dat$playQ==0])
incl<- c(41, 8)
excl<- c(15,4)
d<-as.matrix(rbind.data.frame(incl,excl))
mcnemar.test(d)
```
no difference in reasoning based on play choice

#Exploring difference in Evaluation scores
```{r}
dat$diff<-dat$InclusionNiceScale-dat$ExclusionNiceScale
dat$playQ<-as.numeric(levels(dat$playQ)[dat$playQ])
Anova(glm(playQ~diff*ageMonths,data=dat, family="binomial"))
```
**Note:** Age significantly predicted children's play preferences, but evaluations and their interaction did not. 

##Play Explanation Exploration
```{r}
datPlay<-read.csv("~/Desktop/PIE3P-PlayExplanations.csv",na.strings="0")
datPlayFinal<-subset(datPlay, datPlay$FinalData=="Y")
colnames(datPlay)[1:4]<-c("subj", "FinalData", "ageGroup", "sex")
datPlay$ageGroup<-as.factor(datPlay$ageGroup)
datPlayFinal$OlderYounger <- as.factor(ifelse(datPlayFinal$Age.Group==3 | datPlayFinal$Age.Group==4, "younger", "older"))
```

```{r}
cro(datPlayFinal$PlayChoice, datPlayFinal$Pos.Char)
cro(datPlayFinal$PlayChoice, datPlayFinal$Pos.Char, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Pos.Char, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Neg.Char)
cro(datPlayFinal$PlayChoice, datPlayFinal$Neg.Char, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Neg.Char, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Pos.Feeling)
cro(datPlayFinal$PlayChoice, datPlayFinal$Pos.Feeling, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Pos.Feeling, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Neg.Feeling)
cro(datPlayFinal$PlayChoice, datPlayFinal$Neg.Feeling, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Neg.Feeling, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Inclusion)
cro(datPlayFinal$PlayChoice, datPlayFinal$Inclusion, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Inclusion, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Exclusion)
cro(datPlayFinal$PlayChoice, datPlayFinal$Exclusion, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Exclusion, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Comparison)
cro(datPlayFinal$PlayChoice, datPlayFinal$Comparison, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Comparison, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$MoralTerms)
cro(datPlayFinal$PlayChoice, datPlayFinal$MoralTerms, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$MoralTerms, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$FutureTreatment)
cro(datPlayFinal$PlayChoice, datPlayFinal$FutureTreatment, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$FutureTreatment, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Allow)
cro(datPlayFinal$PlayChoice, datPlayFinal$Allow, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Allow, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$Other)
cro(datPlayFinal$PlayChoice, datPlayFinal$Other, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$Other, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$RestatePlayChoice)
cro(datPlayFinal$PlayChoice, datPlayFinal$RestatePlayChoice, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$RestatePlayChoice, datPlayFinal$OlderYounger)

cro(datPlayFinal$PlayChoice, datPlayFinal$NoExplanation)
cro(datPlayFinal$PlayChoice, datPlayFinal$NoExplanation, datPlayFinal$Age.Group)
cro(datPlayFinal$PlayChoice, datPlayFinal$NoExplanation, datPlayFinal$OlderYounger)
```

"Creating Groups"
```{r}
datPlayFinal$feelings<-NA
for (i in 1:length(datPlayFinal$Subject..)){
datPlayFinal$feelings[i]<- sum(datPlayFinal$Pos.Feeling[i], datPlayFinal$Neg.Feeling[i], na.rm=TRUE)
}
datPlayFinal$characteristics<- NA
for (i in 1:length(datPlayFinal$Subject..)){
datPlayFinal$characteristics[i]<- sum(datPlayFinal$Pos.Char[i],datPlayFinal$Neg.Char[i], na.rm=TRUE)
}
datPlayFinal$gamePlay<- NA
for (i in 1:length(datPlayFinal$Subject..)){
datPlayFinal$gamePlay[i]<- sum(datPlayFinal$Inclusion[i],datPlayFinal$Exclusion[i], na.rm=TRUE)
}
datPlayFinal$abstractConcepts<-NA
for (i in 1:length(datPlayFinal$Subject..)){
datPlayFinal$abstractConcepts[i]<- sum(datPlayFinal$MoralTerms[i],datPlayFinal$FutureTreatment[i], datPlayFinal$Allow[i], na.rm=TRUE)
}

datPlayFinal$decisionMaking<- datPlayFinal$Comparison
```

```{r}
cro(datPlayFinal$PlayChoice, datPlayFinal$characteristics)
cro(datPlayFinal$PlayChoice,datPlayFinal$characteristics,datPlayFinal$OlderYounger)
cro(datPlayFinal$PlayChoice,datPlayFinal$characteristics,datPlayFinal$Age.Group)

cro(datPlayFinal$PlayChoice, datPlayFinal$feelings)
cro(datPlayFinal$PlayChoice,datPlayFinal$feelings,datPlayFinal$OlderYounger)
cro(datPlayFinal$PlayChoice,datPlayFinal$feelings,datPlayFinal$Age.Group)

cro(datPlayFinal$PlayChoice, datPlayFinal$gamePlay)
cro(datPlayFinal$PlayChoice,datPlayFinal$gamePlay,datPlayFinal$OlderYounger)
cro(datPlayFinal$PlayChoice,datPlayFinal$gamePlay,datPlayFinal$Age.Group)

cro(datPlayFinal$PlayChoice, datPlayFinal$abstractConcepts)
cro(datPlayFinal$PlayChoice,datPlayFinal$abstractConcepts,datPlayFinal$OlderYounger)
cro(datPlayFinal$PlayChoice,datPlayFinal$abstractConcepts,datPlayFinal$Age.Group)

cro(datPlayFinal$PlayChoice, datPlayFinal$decisionMaking)
cro(datPlayFinal$PlayChoice,datPlayFinal$decisionMaking,datPlayFinal$OlderYounger)
cro(datPlayFinal$PlayChoice,datPlayFinal$decisionMaking,datPlayFinal$Age.Group)
```

###Exploratory Fisher Tests on Categories
"Characteristics" 
```{r}
olderChar<- c(17,17)
youngerChar<- c(10,25)
ageChar<- as.matrix(rbind(olderChar, youngerChar))
fisher.test(ageChar)
```
```{r}
includerChar<- c(14,35)
excluderChar<- c(3,17)
playChar<- as.matrix(rbind(includerChar, excluderChar))
fisher.test(playChar)
```

"feelings" 
```{r}
olderFeel<- c(0, 34)
youngerFeel<-c(9,26)
ageFeel<- as.matrix(rbind(olderFeel, youngerFeel))
fisher.test(ageFeel)
```
```{r}
includerFeel<- c(5, 44)
excluderFeel<-c(4,16)
playFeel<- as.matrix(rbind(includerFeel, excluderFeel))
fisher.test(playFeel)
```


"Game Play"
```{r}
olderGame<-c(11,23)
youngerGame<-c(6,29)
ageGame<-as.matrix(rbind(olderGame, youngerGame))
fisher.test(ageGame)
```

```{r}
includerGame<- c(14,35)
excluderGame<- c(3,17)
playGame<- as.matrix(rbind(includerGame, excluderGame))
fisher.test(playGame)
```

"Decision Making"
```{r}
olderDecision<- c(11,23)
youngerDecision<- c(2,33)
ageDecide<- as.matrix(rbind(olderDecision, youngerDecision))
fisher.test(ageDecide)

```
```{r}
includeDecision<- c(12,37)
excludeDecision<- c(1,19)
playDecide<- as.matrix(rbind(includeDecision, excludeDecision))
fisher.test(playDecide)
```

"advanced thinking" 
```{r}
olderAdv<- c(12,22)
youngerAdv<-c(1,34)
ageAdv<- as.matrix(rbind(olderAdv, youngerAdv))
fisher.test(ageAdv)
```
```{r}
includeAdv<- c(12,37)
excludeAdv<-c(1,19)
playAdv<- as.matrix(rbind(includeAdv, excludeAdv))
fisher.test(playAdv)
```
##Approach/Avoid Explanation Exploration

```{r}
datAvoid<- read.csv("~/Desktop/PIE3P-AvoidExplanations.csv",na.strings="0")
datAvoidFinal<- subset(datAvoid, datAvoid$FinalData=="Y")
colnames(datAvoid)[1:4]<-c("subj", "FinalData", "ageGroup", "sex")
datAvoidFinal$Age.Group<-as.factor(datAvoidFinal$Age.Group)
datAvoidFinal$OlderYounger <- as.factor(ifelse(datAvoidFinal$Age.Group==3 | datAvoidFinal$Age.Group==4, "younger", "older"))
```
```{r}
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Pos.Char)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Pos.Char, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Pos.Char, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Neg.Char)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Neg.Char, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Neg.Char, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Pos.Feeling)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Pos.Feeling, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Pos.Feeling, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Neg.Feeling)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Neg.Feeling, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Neg.Feeling, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Inclusion)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Inclusion, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Inclusion, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Exclusion)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Exclusion, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Exclusion, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Comparison)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Comparison, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Comparison, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$MoralTerms)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$MoralTerms, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$MoralTerms, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$FutureTreatment)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$FutureTreatment, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$FutureTreatment, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Allow)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Allow, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Allow, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$Other)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Other, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$Other, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$RestatePlayChoice)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$RestatePlayChoice, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$RestatePlayChoice, datAvoidFinal$OlderYounger)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$NoExplanation)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$NoExplanation, datAvoidFinal$Age.Group)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$NoExplanation, datAvoidFinal$OlderYounger)
```

"Creating Groups"
```{r}
datAvoidFinal$feelings<-NA
for (i in 1:length(datAvoidFinal$Subject..)){
datAvoidFinal$feelings[i]<- sum(datAvoidFinal$Pos.Feeling[i], datAvoidFinal$Neg.Feeling[i], na.rm=TRUE)
}
datAvoidFinal$characteristics<- NA
for (i in 1:length(datAvoidFinal$Subject..)){
datAvoidFinal$characteristics[i]<- sum(datAvoidFinal$Pos.Char[i],datAvoidFinal$Neg.Char[i], na.rm=TRUE)
}
datAvoidFinal$gamePlay<- NA
for (i in 1:length(datAvoidFinal$Subject..)){
datAvoidFinal$gamePlay[i]<- sum(datAvoidFinal$Inclusion[i],datAvoidFinal$Exclusion[i], na.rm=TRUE)
}
datAvoidFinal$abstractConcepts<-NA
for (i in 1:length(datAvoidFinal$Subject..)){
datAvoidFinal$abstractConcepts[i]<- sum(datAvoidFinal$MoralTerms[i],datAvoidFinal$FutureTreatment[i], datAvoidFinal$Allow[i], na.rm=TRUE)
}

datAvoidFinal$decisionMaking<- datAvoidFinal$Comparison
```

```{r}
cro(datAvoidFinal$PlayChoice, datAvoidFinal$characteristics)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$characteristics,datAvoidFinal$OlderYounger)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$characteristics, datAvoidFinal$Age.Group)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$feelings)
cro(datAvoidFinal$PlayChoice,datAvoidFinal$feelings,datAvoidFinal$OlderYounger)
cro(datAvoidFinal$PlayChoice,datAvoidFinal$feelings, datAvoidFinal$Age.Group)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$gamePlay)
cro(datAvoidFinal$PlayChoice,datAvoidFinal$gamePlay, datAvoidFinal$OlderYounger)
cro(datAvoidFinal$PlayChoice,datAvoidFinal$gamePlay, datAvoidFinal$Age.Group)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$abstractConcepts)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$abstractConcepts, datAvoidFinal$OlderYounger)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$abstractConcepts, datAvoidFinal$Age.Group)

cro(datAvoidFinal$PlayChoice, datAvoidFinal$decisionMaking)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$decisionMaking, datAvoidFinal$OlderYounger)
cro(datAvoidFinal$PlayChoice, datAvoidFinal$decisionMaking, datAvoidFinal$Age.Group)
```

###Exploratory Fisher's on Categories
"Characteristics" 
```{r}
AolderChar<- c(9,25)
AyoungerChar<- c(4,31)
AageChar<- as.matrix(rbind(AolderChar, AyoungerChar))
fisher.test(AageChar)
```
```{r}
AincluderChar<- c(11,38)
AexcluderChar<- c(2,18)
AplayChar<- as.matrix(rbind(AincluderChar, AexcluderChar))
fisher.test(AplayChar)
```

"feelings" 
```{r}
AolderFeel<- c(1, 33)
AyoungerFeel<-c(3,32)
AageFeel<- as.matrix(rbind(AolderFeel, AyoungerFeel))
fisher.test(AageFeel)

```
```{r}
AincluderFeel<- c(2, 47)
AexcluderFeel<-c(2,18)
AplayFeel<- as.matrix(rbind(AincluderFeel, AexcluderFeel))
fisher.test(AplayFeel)
```


"Game Play"
```{r}
AolderGame<-c(20,14)
AyoungerGame<-c(14,21)
AageGame<-as.matrix(rbind(AolderGame, AyoungerGame))
fisher.test(AageGame)
```

```{r}
AincluderGame<- c(28,21)
AexcluderGame<- c(6,14)
AplayGame<- as.matrix(rbind(AincluderGame, AexcluderGame))
fisher.test(AplayGame)
```

"Decision Making"
```{r}
AolderDecision<- c(1,34)
AyoungerDecision<- c(2,33)
AageDecide<- as.matrix(rbind(AolderDecision, AyoungerDecision))
fisher.test(AageDecide)
```
```{r}
AincludeDecision<- c(2,47)
AexcludeDecision<- c(1,19)
AplayDecide<- as.matrix(rbind(AincludeDecision, AexcludeDecision))
fisher.test(AplayDecide)
```

"advanced thinking" 
```{r}
AolderAdv<- c(10,24)
AyoungerAdv<-c(7,28)
AageAdv<- as.matrix(rbind(AolderAdv, AyoungerAdv))
fisher.test(AageAdv)
```
```{r}
AincludeAdv<- c(13,36)
AexcludeAdv<-c(4,16)
AplayAdv<- as.matrix(rbind(AincludeAdv, AexcludeAdv))
fisher.test(AplayAdv)
```

###NewExploratory Analyses: 11/17
- creating logistic regression to look at association between play choice, age, and category use
```{r}
ageMonths<-cbind.data.frame(dat$subj, dat$ageMonths)
colnames(ageMonths)<- c("Subject..", "ageMonths")
datPlayFinal$PlayChoiceNum<- as.factor(datPlayFinal$PlayChoice)
levels(datPlayFinal$PlayChoiceNum)<-c(0,1)
datPlayFinal$PlayChoiceNum<- as.numeric(levels(datPlayFinal$PlayChoiceNum))[datPlayFinal$PlayChoiceNum]
dp<-right_join(datPlayFinal, ageMonths)
```

"abstract thinking"
```{r}
dp$abstractConcepts<- as.factor(dp$abstractConcepts)
levels(dp$abstractConcepts)<- c(0,1,1)
dp$abstractConcepts<- as.numeric(levels(dp$abstractConcepts))[dp$abstractConcepts]
summary(glm(PlayChoiceNum~ageMonths + abstractConcepts, data=dp, family="binomial"))
summary(glm(PlayChoiceNum~abstractConcepts, data=dp, family="binomial"))
```

"decision making"
```{r}
dp$decisionMaking<- as.factor(dp$decisionMaking)
dp$decisionMaking<-ifelse(is.na(dp$decisionMaking)== TRUE, 0, dp$decisionMaking)
summary(as.factor(dp$decisionMaking))
summary(glm(PlayChoiceNum~ decisionMaking+ ageMonths, data=dp, family="binomial"))
summary(glm(PlayChoiceNum~decisionMaking, data=dp, family="binomial"))
```

"characteristics"
```{r}
dp$characteristics<- as.factor(dp$characteristics)
levels(dp$characteristics)<- c(0,1,1)
dp$characteristics<- as.numeric(levels(dp$characteristics))[dp$characteristics]
summary(glm(PlayChoiceNum~characteristics+ageMonths, data=dp, family="binomial"))
summary(glm(PlayChoiceNum~characteristics, data=dp, family="binomial"))
```

"feelings"
```{r}
summary(as.factor(dp$feelings))
summary(glm(PlayChoiceNum~feelings+ageMonths, data=dp, family="binomial"))
summary(glm(PlayChoiceNum~feelings, data=dp, family="binomial"))
```

