---
title: "PIEDataAnalysis_toShare"
author: "Amanda Mae Woodward"
date: "1/28/2021"
output: html_document
---

```{r loadingLibraries}
library(ggplot2)
library(reshape2)
library(dplyr)
library(tidyverse)
library(lme4)
library(doBy)
library(car)
```

```{r loadingData}
"note: there are problems with the clean data sheets- should use the main coding"
PIE1.4<-read.csv("~/Desktop/PIE analyses/PIE1.4MainAnalysis.csv")
PIE2.4<-read.csv("~/Desktop/PIE analyses/PIE2.4MainAnalysis.csv")
PIE2.5<-read.csv("~/Desktop/PIE analyses/PIE2.5MainAnalysis.csv")

PIE2.6Main<-read.csv("~/Desktop/PIE analyses/PIE2-6MainCoding.csv")
PIE2.6Subj<-subjinfo<- read.csv("~/Desktop/PIE analyses/PIE2-6_subjcoding.csv")

subjinfo<-PIE2.6Subj[,1:12]
colnames(subjinfo)<- c("subj", "id", "sex","dob","dot", "age", "randomization", "ecolor", "eside", "order", "qOrder","finalData")
colnames(PIE2.6Main)<-c("subj", "id", "a1Type", "a1Resp", "q1Type", "q1Resp","q1Exp", "a2Type", "a2Resp", "q2Type", "q2Resp", "q2Exp", "a3Type","a3Resp", "q3Type", "q3Resp", "q3Exp", "PlayQ","MemCheck","overall")
PIE2.6<-left_join(subjinfo,PIE2.6Main[,1:19])
PIE2.6<-subset(PIE2.6,PIE2.6$finalData=="Yes")
```

```{r cleaningPIE14}
for (i in (1:length(colnames(PIE1.4)))){
  PIE1.4[,i]<- as.factor(PIE1.4[,i])
}

PIE1.4$dob2<- as.character(PIE1.4$dob)
PIE1.4$dob<- as.Date(PIE1.4$dob2, format= "%m/%d/%y")
PIE1.4$dot<-as.character(PIE1.4$dot)
PIE1.4$dot<-as.Date(PIE1.4$dot,format= "%m/%d/%y")
PIE1.4$ageDays<-PIE1.4$dot-PIE1.4$dob
PIE1.4$ageMonths<- (PIE1.4$dot-PIE1.4$dob)/30.5
PIE1.4$ageMonths<-as.numeric(PIE1.4$ageMonths)
```

```{r cleaningPIE24}
for(i in(1:length(colnames(PIE2.4)))){
  PIE2.4[,i]<-as.factor(PIE2.4[,i])
}
PIE2.4$dob2<- as.character(PIE2.4$dob)
PIE2.4$dob<- as.Date(PIE2.4$dob2, format= "%m/%d/%y")
PIE2.4$dot<-as.character(PIE2.4$dot)
PIE2.4$dot<-as.Date(PIE2.4$dot,format= "%m/%d/%y")
PIE2.4$ageDays<-PIE2.4$dot-PIE2.4$dob
PIE2.4$ageMonths<- (PIE2.4$dot-PIE2.4$dob)/30.5
```
```{r cleaningPIE25}
for(i in (1:length(colnames(PIE2.5)))){
  PIE2.5[,i]<- as.factor(PIE2.5[,i])
}
PIE2.5$dob2<- as.character(PIE2.5$dob)
PIE2.5$dob<- as.Date(PIE2.5$dob2, format= "%m/%d/%y")
PIE2.5$dot<-as.character(PIE2.5$dot)
PIE2.5$dot<-as.Date(PIE2.5$dot,format= "%m/%d/%y")
PIE2.5$ageDays<-PIE2.5$dot-PIE2.5$dob
PIE2.5$ageMonths<- (PIE2.5$dot-PIE2.5$dob)/30.5
```

```{r cleaningPIE26}
colnames(PIE2.6)
for(i in (1:length(colnames(PIE2.6)))){
  PIE2.6[,i]<- as.factor(PIE2.6[,i])
}
PIE2.6$dob2<- as.character(PIE2.6$dob)
PIE2.6$dob<- as.Date(PIE2.6$dob2, format= "%m/%d/%y")
PIE2.6$dot<-as.character(PIE2.6$dot)
PIE2.6$dot<-as.Date(PIE2.6$dot,format= "%m/%d/%y")
PIE2.6$ageDays<-PIE2.6$dot-PIE2.6$dob
PIE2.6$ageMonths<- (PIE2.6$dot-PIE2.6$dob)/30.5

colnames(PIE2.6)<- c("subj", "id", "sex", "dob", "dot", "age", "randomization", "ewho","eside", "order", "qOrder", "finalData", "allocationtype", "allocatedto", "questiontype", "questionresponse","justification","allocationtype2", "allocatedto2","questiontype2", "questionresponse2", "justication2", "allocationtype3","allocatedto3", "questiontype3", "questionresponse3", "justification3", "questionresponse4", "questionresponse5", "dob2", "ageDays", "ageMonths" )
```

```{r PIE14namingexcluder} 

PIE1.4e0<- subset(PIE1.4,PIE1.4$ewho=="o")
levels(PIE1.4e0$allocatedto)<- c("excluder", "includer")
levels(PIE1.4e0$allocatedto2)<- c("excluder", "includer")
levels(PIE1.4e0$allocatedto3)<- c("excluder", "includer")
levels(PIE1.4e0$questionresponse)<- c(NA,"excluder", "includer")
levels(PIE1.4e0$questionresponse2)<- c(NA,"excluder", "includer")
levels(PIE1.4e0$questionresponse3)<- c(NA,"excluder", "includer")
levels(PIE1.4e0$questionresponse4)<- c("excluder", "includer")

PIE1.4e1<- subset(PIE1.4, PIE1.4$ewho=="y")
levels(PIE1.4e1$allocatedto)<- c("includer", "excluder")
levels(PIE1.4e1$allocatedto2)<- c("includer", "excluder")
levels(PIE1.4e1$allocatedto3)<- c("includer", "excluder")
levels(PIE1.4e1$questionresponse)<- c(NA, "includer", "excluder")
levels(PIE1.4e1$questionresponse2)<- c(NA,"includer", "excluder")
levels(PIE1.4e1$questionresponse3)<- c(NA,"includer", "excluder")
levels(PIE1.4e1$questionresponse4)<- c("includer", "excluder")

PIE1.4F<- rbind.data.frame(PIE1.4e0, PIE1.4e1)  
```

```{r PIE24namingExcluders}
PIE2.4e0<- subset(PIE2.4, PIE2.4$ewho=="b")
levels(PIE2.4e0$allocatedto)<- c("excluder", "includer")
levels(PIE2.4e0$allocatedto2)<- c("excluder", "includer")
levels(PIE2.4e0$allocatedto3)<- c("excluder", "includer")
levels(PIE2.4e0$questionresponse)<- c("excluder", "includer")
levels(PIE2.4e0$questionresponse2)<- c("excluder", "includer")
levels(PIE2.4e0$questionresponse3)<- c("excluder", "includer")
levels(PIE2.4e0$questionresponse4)<- c("excluder", "includer")
levels(PIE2.4e0$questionresponse5)<- c(NA,"excluder", "includer")
PIE2.4e1<- subset(PIE2.4, PIE2.4$ewho=="g")
levels(PIE2.4e1$allocatedto)<- c("includer", "excluder")
levels(PIE2.4e1$allocatedto2)<- c("includer", "excluder")
levels(PIE2.4e1$allocatedto3)<- c("includer", "excluder")
levels(PIE2.4e1$questionresponse)<- c("includer", "excluder")
levels(PIE2.4e1$questionresponse2)<- c("includer", "excluder")
levels(PIE2.4e1$questionresponse3)<- c("includer", "excluder")
levels(PIE2.4e1$questionresponse4)<- c("includer", "excluder")
levels(PIE2.4e1$questionresponse5)<- c(NA,"includer", "excluder")
PIE2.4F<- rbind.data.frame(PIE2.4e0,PIE2.4e1)
```

```{r PIE25namingExcluders}
PIE2.5e0<- subset(PIE2.5, PIE2.5$ewho=="b")
levels(PIE2.5e0$allocatedto)<- c("excluder", "includer")
levels(PIE2.5e0$allocatedto2)<- c("excluder", "includer")
levels(PIE2.5e0$allocatedto3)<- c("excluder", "includer")
levels(PIE2.5e0$questionresponse)<- c("excluder", "includer")
levels(PIE2.5e0$questionresponse2)<- c("excluder", "includer")
levels(PIE2.5e0$questionresponse3)<- c("excluder", "includer")
levels(PIE2.5e0$questionresponse4)<- c("excluder", "includer")
levels(PIE2.5e0$questionresponse5)<- c("excluder", "includer")
PIE2.5e1<- subset(PIE2.5, PIE2.5$ewho=="g")
levels(PIE2.5e1$allocatedto)<- c("includer", "excluder")
levels(PIE2.5e1$allocatedto2)<- c("includer", "excluder")
levels(PIE2.5e1$allocatedto3)<- c("includer", "excluder")
levels(PIE2.5e1$questionresponse)<- c("includer", "excluder")
levels(PIE2.5e1$questionresponse2)<- c("includer", "excluder")
levels(PIE2.5e1$questionresponse3)<- c("includer", "excluder")
levels(PIE2.5e1$questionresponse4)<- c("includer", "excluder")
levels(PIE2.5e1$questionresponse5)<- c("includer", "excluder")
PIE2.5F<- rbind.data.frame(PIE2.5e0,PIE2.5e1)
```

```{r PIE26namingExcluders}
PIE2.6e0<- subset(PIE2.6, PIE2.6$ewho=="Blue")
levels(PIE2.6e0$allocatedto)<- c("excluder", "includer")
levels(PIE2.6e0$allocatedto2)<- c("excluder", "includer")
levels(PIE2.6e0$allocatedto3)<- c("excluder", "includer")
levels(PIE2.6e0$questionresponse)<- c("excluder", "includer")
levels(PIE2.6e0$questionresponse2)<- c("excluder", "includer")
levels(PIE2.6e0$questionresponse3)<- c("excluder", "includer")
levels(PIE2.6e0$questionresponse4)<- c("excluder", "includer")
levels(PIE2.6e0$questionresponse5)<- c("excluder", "includer")
PIE2.6e1<- subset(PIE2.6, PIE2.6$ewho=="Green")
levels(PIE2.6e1$allocatedto)<- c("includer", "excluder")
levels(PIE2.6e1$allocatedto2)<- c("includer", "excluder")
levels(PIE2.6e1$allocatedto3)<- c("includer", "excluder")
levels(PIE2.6e1$questionresponse)<- c("includer", "excluder")
levels(PIE2.6e1$questionresponse2)<- c("includer", "excluder")
levels(PIE2.6e1$questionresponse3)<- c("includer", "excluder")
levels(PIE2.6e1$questionresponse4)<- c("includer", "excluder")
levels(PIE2.6e1$questionresponse5)<- c("includer", "excluder")
PIE2.6F<- rbind.data.frame(PIE2.6e0,PIE2.6e1)
```

```{r allocationSums}
PIE1.4F$allocationSum<- rep(NA, nrow(PIE1.4F))
for (i in 1:nrow(PIE1.4F)){
  PIE1.4F$allocationSum[i]<-sum(PIE1.4F$allocatedto[i]=="includer", PIE1.4F$allocatedto2[i]=="includer", PIE1.4F$allocatedto3[i]=="includer")
}

PIE2.4F$allocationSum<- rep(NA, nrow(PIE2.4F))
for (i in 1:nrow(PIE2.4F)){
  PIE2.4F$allocationSum[i]<-sum(PIE2.4F$allocatedto[i]=="includer", PIE2.4F$allocatedto2[i]=="includer", PIE2.4F$allocatedto3[i]=="includer")
}

PIE2.5F$allocationSum<- rep(NA, nrow(PIE2.5F))
for (i in 1:nrow(PIE2.5F)){
  PIE2.5F$allocationSum[i]<-sum(PIE2.5F$allocatedto[i]=="includer", PIE2.5F$allocatedto2[i]=="includer", PIE2.5F$allocatedto3[i]=="includer")
}

PIE2.6F$allocationSum<- rep(NA, nrow(PIE2.6F))
for (i in 1:nrow(PIE2.6F)){
  PIE2.6F$allocationSum[i]<-sum(PIE2.6F$allocatedto[i]=="includer", PIE2.6F$allocatedto2[i]=="includer", PIE2.6F$allocatedto3[i]=="includer")
}
```
# PIE1.4 Data Analyses
###Question: Do children prefer includers over excluders (as evidenced by resource allocations)?
####Preliminary Analyses
```{r 1.4AllocationPrelim}
aSum1.4<- lm(allocationSum~ewho+eside+order+sex+ageMonths, data=PIE1.4F)
summary(aSum1.4)
```
**Interpretation:** No counterbalancing factors influence children's allocation choices. 

####Analysis
```{r 1.4Allocation}
t.test(PIE1.4F$allocationSum,mu=1.5)
p.adjust(1, n = 5, method="bonferroni")
```

###Do children's first allocation choices indicate a preference for either character? 
####Preliminary 
```{r 1.4firstAllocation, include=FALSE}
PIE1.4F$allocatedFirst<-PIE1.4F$allocatedto
levels(PIE1.4F$allocatedFirst)<- c(0,1)
PIE1.4F$allocatedFirst<- as.numeric(levels(PIE1.4F$allocatedFirst))[PIE1.4F$allocatedFirst]
```
```{r 1.4firstAllocationPrelim}
aFirst1.4<- glm(allocatedFirst~ewho+eside+order+sex, data=PIE1.4F, family="binomial")
summary(aFirst1.4)
```
**Interpretation:** No counterbalancing factors predicted children's first allocation choice. 

####Analysis
```{r 1.4FirstAllocation}
summary(as.factor(PIE1.4F$allocatedFirst))
binom.test(12,32)
```
**Interpretation:** Children did not allocate the first item to either character more often than chance (12 of 32, p = 0.21)

###Question: Do children indicate the excluder is meaner than the includer more often than chance?"

**preliminary analysis**

```{r 1.4meanPrelim}
Mean1.4<- glm(questionresponse~ewho+eside+order+sex, data=PIE1.4F, family="binomial")
summary(Mean1.4)
```
**Interpretation:** Counterbalance factors did not predict who children identified as meaner

**analysis**

```{r 1.4Mean}
summary(PIE1.4F$questionresponse)
binom.test(18,31)
```
**Interpretation:** Children do not indicate the excluder is the meaner character more often than chance (18 of 31, p = 0.47)

###Question: Do children indicate that the includer is a better sharer than the excluder more often than chance?

**preliminary analysis**

```{r 1.4SharesetupPrelim, include=FALSE}
levels(PIE1.4F$questionresponse2)<- c(0,1)
PIE1.4F$questionresponse2<- as.numeric(levels(PIE1.4F$questionresponse2))[PIE1.4F$questionresponse2]
```
```{r 1.4SharePrelim}
Share1.4<- glm(questionresponse2~ewho + eside+order+sex, data=PIE1.4F, family="binomial")
summary(Share1.4)
```
**Interpretation** counterbalance factors do not predict whether children will indicate the includer is a better sharer.

**analysis**

```{r 1.4Sharer}
summary(as.factor(PIE1.4F$questionresponse2))
binom.test(19,31)
```
**Interpretation:** Children do not indicate the includer is the better sharing character more often than chance (19 of 31, p = .28)

###Question: Do children indicate the includer has more friends than the excluder more often than chance?

**preliminary analysis**

```{r 1.4FriendsPrelimsetup, include=FALSE}
levels(PIE1.4F$questionresponse3)<- c(0,1)
PIE1.4F$questionresponse3<- as.numeric(levels(PIE1.4F$questionresponse3))[PIE1.4F$questionresponse3]
```
```{r 1.4FriendsPrelim}
Friends1.4<- glm(questionresponse3~ewho +eside+order+sex, data=PIE1.4F)
summary(Friends1.4)
```
**Interpretation:** Counterbalancing factorsdid not predict children's choice of who has more friends

**analysis**

```{r 1.4Friends}
summary(as.factor(PIE1.4F$questionresponse3))
binom.test(19,31)
```
**Interpretation:** Children do not indicate the includer has more friends more often than chance (19 of 31, p =.28)

###Question: Do children indicate that Horsey should play with the includer more often than chance?

**preliminary analysis**

```{r 1.4HorsePrelimsetup, include=FALSE}
levels(PIE1.4F$questionresponse4)<- c(0,1)
PIE1.4F$questionresponse4<- as.numeric(levels(PIE1.4F$questionresponse4))[PIE1.4F$questionresponse4]
```
```{r 1.4HorsePrelim}
ThirdParty1.4<- glm(questionresponse4~ewho+eside+order+sex, data=PIE1.4F)
summary(ThirdParty1.4)

```
**Interpretation:** Counterbalancing factors are not significant predictors of children's third-party suggestions

**analysis**

```{r 1.4Horse}
summary(as.factor(PIE1.4F$questionresponse4))
binom.test(18,32)
```
**Interpretation:** Children do not indicate that horsey should play with the includers more than chance (18 of 32, p=.59)

##PIE1.4 Exploratory Analysis- Sharer as a (rough) manipulation check
```{r 1.4SharerSubset, include=FALSE}
PIE1.4Share<- subset(PIE1.4F, PIE1.4F$questionresponse2==1)
```
###Question: Do children prefer includers over excluders (as evidenced by resource allocations)?

**preliminary analysis**

```{r 1.4Share-AllocationPrelim}
ExaSum1.4<- lm(allocationSum~ewho+eside+order+sex, data=PIE1.4Share)
summary(ExaSum1.4)
```
**Interpretation:** Children allocate more items to the yellow puppets and to the puppets on the right. The intercept is also significant.  

**analysis**

```{r 1.4Share-Allocation}
t.test(PIE1.4Share$allocationSum, mu=1.5)
```
Interpretation: There is no significant difference between the number of items children allocate to the includer (t=.96, df=18, p = .35)

###Question: Do children's first resource allocations indicate a preference for one character over another?

**preliminary setup**

```{r 1.4ShareFirstAllocation-Prelimsetup, include=FALSE}
PIE1.4Share$allocatedFirst<-PIE1.4Share$allocatedto
levels(PIE1.4Share$allocatedFirst)<- c(0,1)
PIE1.4Share$allocatedFirst<- as.numeric(levels(PIE1.4Share$allocatedFirst))[PIE1.4Share$allocatedFirst]
```
```{r 1.4ShareFirstAllocation-Prelim}
ExaFirst1.4<- glm(allocatedFirst~ewho+eside+order+sex, data=PIE1.4Share)
summary(ExaFirst1.4)
```
**Interpretation:** The counterbalancing factors did not predict children's first allocation choice. 

**analysis**
```{r 1.4ShareFirstAllocation}
summary(as.factor(PIE1.4Share$allocatedFirst))
binom.test(8,19)
```
**Interpretation:** children do not prefer the includer in their first allocation choices (8 of 19, p = .65)

###Question: Do children indicate the excluder is meaner than the includer more often than chance?

**preliminary analysis**

```{r 1.4ShareMean-Prelim}
ExMean1.4<-glm(questionresponse2~eside+ewho+order+sex, data=PIE1.4Share, family="binomial")
summary(ExMean1.4)
```
**Interpretation:** Counterbalancing factors do not predict children's choices of who is meaner.

**analysis**

```{r 1.4ShareMean}
summary(PIE1.4Share$questionresponse)
binom.test(18,19)
```
**Interpretation:** Children identified the excluder as the meaner character more often than chance (18 of 19, p<0.001)

###Question: Do children indicate the includer has more friends than the excluder more often than chance?"

**preliminary analysis**

```{r 1.4ShareFriends-Prelim}
ExFriends1.4<- lm(questionresponse3~ewho+eside+order+sex,data=PIE1.4Share)
summary(ExFriends1.4)
```
**Interpretation:** Counterbalancing factors do not predict children's choice of who has more friends.

**analysis**

```{r 1.4ShareFriends}
summary(as.factor(PIE1.4Share$questionresponse3))
binom.test(11,19)
```
**Interpretation:** Children do not indicate the includer has more friends more often than chance (11 of 19, p = .64)

###Question: Do children indicate that Horsey should play with the includer more often than chance?

**preliminary analysis**

```{r 1.4ShareHorse-Prelim}
ExThirdParty1.4<- lm(questionresponse4~ewho +eside+ order+ sex, data=PIE1.4Share)
summary(ExThirdParty1.4)
```
**Interpretation:** Counterbalancing factors do not predict children's play partner choice. the intercept is significant.

**analysis**

```{r 1.4ShareHorse}
summary(as.factor(PIE1.4Share$questionresponse4))
binom.test(14,19)
```
**Interpretation:** Children do not suggest Horsey play with the includer over the excluder (14 of 19, p = 0.06). 

#PIE 2- All participants (Supplemental Material)
Note: for PIE 2, the questions were not asked in a fixed order. In order to run analyses, I need to clean the data and create columns for the separate mean, nice, and sharer questions. 
```{r}
PIE2.4F$Mean<- NA
PIE2.4F$Nice<- NA
PIE2.4F$Share<-NA

for (j in seq(60,70, 5)){
  for (i in 1:nrow(PIE2.4F)){
    if(PIE2.4F[i,j]=="m"){
      PIE2.4F$Mean[i]<- levels(PIE2.4F[,(j+1)])[PIE2.4F[i,(j+1)]]}
    if(PIE2.4F[i,j]=="n"){
      PIE2.4F$Nice[i]<-levels(PIE2.4F[,(j+1)])[PIE2.4F[i,(j+1)]]}
    if(PIE2.4F[i,j]=="s"){
      PIE2.4F$Share[i]<-levels(PIE2.4F[,(j+1)])[PIE2.4F[i,(j+1)]]}
  }
}  
PIE2.4F$horse<- PIE2.4F$questionresponse4
PIE2.4F$mem<- PIE2.4F$questionresponse5
```
```{r}
PIE2.5F$Mean<- NA
PIE2.5F$Nice<- NA
PIE2.5F$Share<-NA
for (j in seq(63,73, 5)){
  for (i in 1:nrow(PIE2.5F)){
    if(PIE2.5F[i,j]=="m"){
      PIE2.5F$Mean[i]<- levels(PIE2.5F[,(j+1)])[PIE2.5F[i,(j+1)]]}
    if(PIE2.5F[i,j]=="n"){
      PIE2.5F$Nice[i]<-levels(PIE2.5F[,(j+1)])[PIE2.5F[i,(j+1)]]}
    if(PIE2.5F[i,j]=="s"){
      PIE2.5F$Share[i]<-levels(PIE2.5F[,(j+1)])[PIE2.5F[i,(j+1)]]}
  }
}
PIE2.5F$horse<- PIE2.5F$questionresponse4
PIE2.5F$mem<- PIE2.5F$questionresponse5

```

```{r}
PIE2.6F$Mean<- NA
PIE2.6F$Nice<- NA
PIE2.6F$Share<-NA
for (j in seq(15,25, 5)){
  for (i in 1:nrow(PIE2.6F)){
    if(PIE2.6F[i,j]=="meaner"){
      PIE2.6F$Mean[i]<- levels(PIE2.6F[,(j+1)])[PIE2.6F[i,(j+1)]]}
    if(PIE2.6F[i,j]=="nicer"){
      PIE2.6F$Nice[i]<-levels(PIE2.6F[,(j+1)])[PIE2.6F[i,(j+1)]]}
    if(PIE2.6F[i,j]=="sharer"){
      PIE2.6F$Share[i]<-levels(PIE2.6F[,(j+1)])[PIE2.6F[i,(j+1)]]}
  }
}
PIE2.6F$horse<- PIE2.6F$questionresponse4
PIE2.6F$mem<- PIE2.6F$questionresponse5
```
```{r combinev2}
PIE2.4F$study<-4
PIE2.5F$study<-5
PIE2.6F$study<-6
Fours<- cbind.data.frame(PIE2.4F[,1:7],PIE2.4F[,51], PIE2.4F[,86:93])
colnames(Fours)[8]<-"firstAllocation"
Fives<- cbind.data.frame(PIE2.5F[,1:7], PIE2.5F[,52], PIE2.5F[,91:98])
colnames(Fives)[8]<-"firstAllocation"
Sixes<- cbind.data.frame(PIE2.6F[,2],PIE2.6F[,1],PIE2.6F[,3:4], PIE2.6F[,8:10], PIE2.6F[,14], PIE2.6F[,32:39])
colnames(Sixes)<-c("id", "subj", "sex", "dob","ewho","eside","order","firstAllocation", "ageMonths", "allocationSum", "Mean", "Nice", "Share", "horse","mem", "study")
PIEv2<- rbind.data.frame(Fours,Fives,Sixes)
levels(PIEv2$sex)<- c("f", "m", "f", "m")
levels(PIEv2$eside)<-c("l", "r", "l", "r")
```
### Question: Do children allocate more resources to the includer or excluder? 

**preliminary analyses**
```{r}
aSumAll<-lm(allocationSum~ewho+eside+order+sex +ageMonths, data=PIEv2)
summary(aSumAll)
```
**Interpretation:** No counterbalancing factors influenced children's allocation choices

**analyses**
```{r}
t.test(PIEv2$allocationSum, mu=1.5)
```
**Interpretation:** Children did not allocate items differently between includers and excluders

###Question: Do children's first resource allocations indicate a preference for one character over another?

**preliminary setup**

```{r 1.4ShareFirstAllocation-Prelimsetup, include=FALSE}
levels(PIEv2$firstAllocation)<- c(0,1)
PIEv2$firstAllocation <- as.numeric(levels(PIEv2$firstAllocation))[PIEv2$firstAllocation]
```
```{r 1.4ShareFirstAllocation-Prelim}
a1v2<- glm(firstAllocation~ewho+eside+order+sex, data=PIEv2, family="binomial")
summary(a1v2)
```
**Interpretation:** No counterbalancing factors influenced children's allocation choices

**analysis**
```{r}
summary(as.factor(PIEv2$firstAllocation))
binom.test(39, 96)
```
**Interpretation:** Children's first allocation choices did not favor either character. 

###Question: Do children's combined mean/nice responses indicate the includer is more positive?
```{r}
PIEv2$Mean<-as.factor(PIEv2$Mean)
levels(PIEv2$Mean)<- c(1,0)
PIEv2$Mean<-as.numeric(levels(PIEv2$Mean))[PIEv2$Mean]
PIEv2$Nice<-as.factor(PIEv2$Nice)
levels(PIEv2$Nice)<- c(0,1)
PIEv2$Nice<-as.numeric(levels(PIEv2$Nice))[PIEv2$Nice]
PIEv2$Pos<- PIEv2$Mean + PIEv2$Nice
```

**preliminary analyses**
```{r}
v2lmPos<- lm(Pos~ ewho+eside+order +sex + ageMonths, data=PIEv2)
summary(v2lmPos)
```
**Interpretation:** Males were less likely to view includers more positively than excluders 

**analysis**
```{r}
t.test(PIEv2$Pos, mu=1)
```
**Interpretation:** Children did not rate exluders differently than includers

###Question: Do children indicate the excluder is meaner than the includer more often than chance?

**preliminary analysis**

```{r CombMeanerPrelim}
v2Mean<-glm(Mean~ewho+eside+order+sex+ ageMonths,data=PIEv2, family="binomial")
summary(v2Mean)
```
**Interpretation:** Males were less likely to view excluders as meaner than females

**analysis**
```{r CombMeaner}
summary(as.factor(PIEv2$Mean))
binom.test(54,96)
```
**Interpretation:** Children do not state that the excluder is meaner than the includer more often than chance (54 of 96, p =0.26). 

###Question: Do children indicate the includer is nicer than the excluder more often than chance?

**preliminary analysis**

```{r CombMeanerPrelim}
v2Nice<-glm(Nice~ewho+eside+order+sex+ ageMonths,data=PIEv2, family="binomial")
summary(v2Nice)
```
**Interpretation:** None of the counterbalancing factors significantly predicted children's choice of which puppet was nicer

**analysis**
```{r CombMeaner}
summary(as.factor(PIEv2$Nice))
binom.test(50,96)
```
**Interpretation:** Children do not state that the includer is nicer than the excluder more often than chance (50 of 96, p =0.76). 

###Question: Do children indicate that the includer is a better sharer than the excluder more often than chance?"

**preliminary analysis**
```{r include=FALSE}
PIEv2$Share<- as.factor(PIEv2$Share)
levels(PIEv2$Share)<-c(0,1) 
PIEv2$Share<-as.numeric(levels(PIEv2$Share))[PIEv2$Share]
```
```{r CombsharerPrelim}
v2Share<-glm(Share~ewho+eside+order+sex +ageMonths,data=PIEv2, family="binomial")
summary(v2Share)
```
**Interpretation:** None of the counterbalancing factors significantly predicted children's choice of which puppet was a better sharer

**analysis**

```{r CombShare}
summary(as.factor(PIEv2$Share))
binom.test(55,96)
```
**Interpretation:** Children do not think the includer is a better sharer  (55 of 96, p = .18). 

###Question: Do children indicate that Horsey should play with the includer more often than chance?

**preliminary analysis**
```{r include=FALSE}
PIEv2$horse<- as.factor(PIEv2$horse)
levels(PIEv2$horse)<-c(0,1) 
PIEv2$horse<-as.numeric(levels(PIEv2$horse))[PIEv2$horse]
```
```{r CombHorsePrelim}
v2horse<-glm(horse~ewho+eside+order+sex +ageMonths,data=PIEv2, family="binomial")
summary(v2horse)
```
**Interpretation:** None of the counterbalancing factors significantly predicted children's choice of which puppet was a better sharer

**analysis**

```{r CombHorse}
summary(as.factor(PIEv2$horse))
binom.test(58,96)
```
**Interpretation:** Children did not recommend that horsey play with the includer more than chance( 58 of 96, p =0.051) 

### Question: Do children answer the memory check correctly (the includer played with them more?)

**preliminary analysis**

```{r, include=FALSE}
summary(PIEv2$mem)
PIEv2$mem<- as.factor(PIEv2$mem)
levels(PIEv2$mem)<- c(0,1)
PIEv2$mem<-as.numeric(levels(PIEv2$mem))[PIEv2$mem]
```
```{r}
v2Mem<- glm(mem~ewho + eside+ order + sex + ageMonths, data=PIEv2, family="binomial")
summary(v2Mem)
```
**Interpretation::** No counterbalancing factors predicted children's memory check responses

**analysis**

```{r}
summary(as.factor(PIEv2$mem))
binom.test(68, 96)
```
**Interpretation:** Children answered the memory check correctly more often than chance

#PIE 2 Analyses: Memory Check Correct
Subsequent analyses include only the participants who accurately answered the memory check question.

```{r}
PIEv2MemCorr<-subset(PIEv2, PIEv2$mem==1)
```

### Question: Do children allocate more resources to the includers? 

**preliminary analyses**
```{r}
v2MCallocation<- lm(allocationSum~ewho+eside+ order + sex + ageMonths, data=PIEv2MemCorr)
summary(v2MCallocation)
```
**Interpretation:** No counterbalancing factors predicted children's allocations

**analyses**
```{r}
t.test(PIEv2MemCorr$allocationSum, mu=1.5)
```
**Interpretation:** Children did not favor either character with their allocation choices. 

###Question: Do children's first resource allocations indicate a preference for one character over another?

**preliminary analysis**

```{r MemCombFirstAllocationPrelim}
v2MCFirst<- lm(firstAllocation~ewho+eside+order+sex + ageMonths, data= PIEv2MemCorr)
summary(v2MCFirst)
```
**Interpretation:** No counterbalancing factors significantly predicted children's first allocation choice.  

**analysis**
```{r MemCombFirstAllocation}
summary(as.factor(PIEv2MemCorr$firstAllocation))
binom.test(31,68)
```
**Interpretation:** Children did not favor either character with their first allocation. 

###Do children attribute more positive characteristics to includers? 

**preliminary analysis**
```{r}
v2MCPos<- lm(Pos~ewho+eside+order + sex+ ageMonths, data=PIEv2MemCorr)
summary(v2MCPos)
```
**Interpretation:** No counterbalancing factors were significant predictors of children's responses

**analysis**
```{r}
t.test(PIEv2MemCorr$Pos, mu=1)
```
**Interpretation:** Children significantly attributed more positive characteristics to includers than excluders 

###Question: Do children indicate the excluder is meaner than the includer more often than chance?

**preliminary analysis**

```{r MemCombMeanerPrelim}
v2MCMean<-glm(Mean~ewho+eside+order+sex + ageMonths,data=PIEv2MemCorr, family="binomial")
summary(v2MCMean)
```
**Interpretation:** No counterbalancing factors significantly predicted children's choice of which puppet was meaner

**analysis**

```{r MemCombMeaner}
summary(as.factor(PIEv2MemCorr$Mean))
binom.test(46,68)
```
**Interpretation:** Children state that the excluder is meaner than the includer more often than chance (46 of 68, p <0.01). 

###Question: Do children indicate the includer is nicer than the excluder more often than chance?

**preliminary analysis**

```{r MemCombNicerPrelim}
v2MCNice<-glm(Nice~ewho+eside+order+sex + ageMonths,data=PIEv2MemCorr, family="binomial")
summary(v2MCNice)
```
**Interpretation:** No counterbalancing factors significantly predicted children's choice of which puppet was nicer 

**analysis**
```{r MemCombNicer}
summary(as.factor(PIEv2MemCorr$Nice))
binom.test(44,68)
```
**Interpretation:** Children state that the includer is nicer than the includer more often than chance (46 of 68, p = 0.02).

###Question: Do children indicate the includer is a better sharer than the excluder more often than chance?

**preliminary analysis**

```{r MemCombSharePrelim}
v2MCShare<-glm(Share~ewho+eside+order+sex + ageMonths,data=PIEv2MemCorr, family="binomial")
summary(v2MCShare)
```
**Interpretation:** No counterbalancing factors significantly predicted children's choice of which puppet was nicer 

**analysis**
```{r MemCombSharer}
summary(as.factor(PIEv2MemCorr$Share))
binom.test(46,68)
```
**Interpretation:** Children state that the includer is nicer than the includer more often than chance (46 of 68, p < 0.01).

###Question: Do children indicate that Horsey should play with the includer more often than chance?

**preliminary analysis**

```{r MemCombSharePrelim}
v2MChorse<-glm(horse~ewho+eside+order+sex + ageMonths,data=PIEv2MemCorr, family="binomial")
summary(v2MChorse)
```
**Interpretation:** No counterbalancing factors significantly predicted children's choice of which puppet was nicer 

**analysis**
```{r MemCombSharer}
summary(as.factor(PIEv2MemCorr$horse))
binom.test(49,68)
```
**Interpretation:** Children recommend that the novel character should play with the includer more often than chance (46 of 68, p < 0.01).
